The Perils of Exploration under Competition: \\ A Computational Modeling Approach

### 2020-09-04 journal paper/ec19paper/content/inverted_u.tex
update figures

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\footnotesize
\begin{table*}[t]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c||}{Heavy-Tail}
  & \multicolumn{3}{c|}{Needle-in-Haystack}\\
  \hline
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
\TS vs \DG
  & \makecell{\textbf{0.29} $\pm$0.03\\ \Eeog 55 (0)}
  & \makecell{\textbf{0.72} $\pm$0.02\\ \Eeog 570 (0)}
  & \makecell{\textbf{0.76} $\pm$0.02\\ \Eeog 620 (99)}
  %%
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 200 (27)}
  & \makecell{\textbf{0.6} $\pm$0.03\\ \Eeog 370 (0)}
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 580 (122)}
  \\
\hline
  $\TS$ vs $\DEG$
  & \makecell{\textbf{0.3} $\pm$0.03\\ \Eeog 37 (0)}
  & \makecell{\textbf{0.88} $\pm$0.01\\ \Eeog 480 (0)}
  & \makecell{\textbf{0.9} $\pm$0.01\\ \Eeog 570 (114)}
  %%
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 150 (14)}
  & \makecell{\textbf{0.52} $\pm$0.03\\ \Eeog 460 (79)}
  & \makecell{\textbf{0.56} $\pm$0.02\\ \Eeog 740 (628)}
  \\
\hline
  $\DG$ vs $\DEG$
  & \makecell{\textbf{0.62} $\pm$0.03\\ \Eeog 410 (7)}
  & \makecell{\textbf{0.6} $\pm$0.02\\ \Eeog 790 (762)}
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 730 (608)}
  %%
  & \makecell{\textbf{0.46} $\pm$0.03\\ \Eeog 340 (129)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 650 (408)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 690 (467)}
  \\
   \hline
\end{tabular}
\normalsize
\caption{{\bf Simultaneous Entry}, for Heavy-Tail and Needle-in-Haystack instances. Each cell describes a game between two algorithms, call them Alg1 vs. Alg2, for a particular value of the warm start $T_0$. Line 1 in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG.
Line 2 specifies the ``effective end of game" (\Eeog): the average and the median (in brackets). The time horizon is $T=2000$.}
\label{sim_table}
\end{table*}

\normalsize
Our main experiments are with the duopoly game defined in Section~\ref{sec:model}. As the ``intensity of competition" varies from  monopoly to ``incumbent" to simultaneous entry duopoly to ``late entrant", we find a stylized inverted-U relationship as in Figure~\ref{fig:inverted-U}. More formally, we look for equilibria in the duopoly game, where each firm's choices are limited to \DynamicGreedy, \DynamicEpsGreedy and \Thompson. We do this for each ``intensity level" and each MAB instance, and look for findings that are consistent across MAB instances. For cleaner results, we break ties towards less advanced algorithms (as they tend to have lower adoption costs \cite{DS-arxiv}). Note that \DynamicGreedy is trivially the dominant strategy under monopoly.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
 % \hline
 % & \multicolumn{3}{c|}{Uniform} \\
\hline
   & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\ \hline
\TS vs \DG
  & \makecell{\textbf{0.46} $\pm$0.03}
    & \makecell{\textbf{0.52} $\pm$0.02}
    & \makecell{\textbf{0.6} $\pm$0.02} \\ \hline
\TS vs \DEG
    & \makecell{\textbf{0.41} $\pm$0.03}
    & \makecell{\textbf{0.51} $\pm$0.02}
    & \makecell{\textbf{0.55} $\pm$0.02} \\ \hline
\DG vs \DEG
    & \makecell{\textbf{0.51} $\pm$0.03}
    & \makecell{\textbf{0.48} $\pm$0.02}
    & \makecell{\textbf{0.45} $\pm$0.02} \\\hline
\end{tabular}
\caption{{\bf Simultaneous entry}, for the Uniform MAB instance. Semantics are the same as in Table \ref{sim_table}.}
\label{tab:duopoly_unif}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$
    & \makecell{\textbf{0.003}$\pm$0.003}
    & \makecell{\textbf{0.083}$\pm$0.02}
    & \makecell{\textbf{0.17}$\pm$0.02} \\\hline
$\DEG$
    & \makecell{\textbf{0.045}$\pm$0.01}
    & \makecell{\textbf{0.25}$\pm$0.02}
    & \makecell{\textbf{0.23}$\pm$0.02} \\\hline
$\DG$
    & \makecell{\textbf{0.12}$\pm$0.02}
    & \makecell{\textbf{0.36}$\pm$0.03}
    & \makecell{\textbf{0.3}$\pm$0.02} \\\hline
\end{tabular}
\captionsetup{labelformat=empty}
\caption{Market share of row player (entrant), 200 round head-start, Heavy-Tail Instance}
%\caption{{\bf Temporary monopoly}, with $X=200$ (and $T_0=20$), for the Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the row) and the incumbent's algorithm (the column). The cell specifies the entrant's market share (fraction of rounds in which it was chosen) for the rounds in which he was present. We give the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\label{tab:ht-incum}
\end{table}
\OMIT{
\begin{table}[h]
\centering
\caption{Heavy Tail}
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$
    & \makecell{\textbf{0.50, 0.50}}
    & \makecell{\textbf{0.3, 0.7}}
    & \makecell{\textbf{0.29, 0.71}} \\\hline
$\DEG$
    & \makecell{\textbf{0.7, 0.3}}
    & \makecell{\textbf{0.50, 0.50}}
    & \makecell{\textbf{0.38, 0.62}} \\\hline
$\DG$
    & \makecell{\textbf{0.71, 0.29}}
    & \makecell{\textbf{0.62, 0.38}}
    & \makecell{\textbf{0.50, 0.50}} \\\hline
\end{tabular}
\end{table}

@@

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}
      \draw[->] (-.5,0) -- (7,0) node[right] {};
      \draw[->] (0,-.5) -- (0,3) node[above] {Better algorithms};
      \draw[scale=0.6,domain=0.7:9.8,smooth,variable=\x,blue, line width=0.3mm] plot ({\x},{4.5 - 0.18 * (\x - 5.25)^2});
     \node[below] at (0.7, -0.22) {\footnotesize monopoly};
     \node[below] at (2.8, -0.2) {\footnotesize incumbent};
     \node[below] at (4.8, -0.22) {\footnotesize sim. entry};
     \node[below] at (6.2, -0.2) {\footnotesize entrant};
 \end{tikzpicture}
 \caption{A stylized ``inverted-U relationship" between strength of competition and ``level of innovation".}
\label{fig:inverted-U-expts}
\end{center}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{ec19paper/figures/unif_eq_welfare}
\includegraphics[scale=0.35]{ec19paper/figures/ht_eq_welfare}
\caption{Smoothed welfare plots resulting from equilibrium strategies in the different market structures. Note that welfare at $t = 0$ incorporates the regret incurred during the incumbent and warm start periods. The Thompson Sampling trajectory displays the regret incurred by running Thompson Sampling in isolation on the given instances.}
\label{eq_regret}
\end{figure}

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table*}[t]
\centering
\begin{adjustbox}{width=\textwidth,center}
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c||}{Heavy-Tail}
  & \multicolumn{3}{c|}{Needle-in-Haystack}\\
  \hline
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500
  & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
\TS vs \DG
  & \makecell{\textbf{0.29} $\pm$0.03\\ \Eeog 55 (0)}
  & \makecell{\textbf{0.72} $\pm$0.02\\ \Eeog 570 (0)}
  & \makecell{\textbf{0.76} $\pm$0.02\\ \Eeog 620 (99)}
  %%
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 200 (27)}
  & \makecell{\textbf{0.6} $\pm$0.03\\ \Eeog 370 (0)}
  & \makecell{\textbf{0.64} $\pm$0.03\\ \Eeog 580 (122)}
  \\
\hline
  $\TS$ vs $\DEG$
  & \makecell{\textbf{0.3} $\pm$0.03\\ \Eeog 37 (0)}
  & \makecell{\textbf{0.88} $\pm$0.01\\ \Eeog 480 (0)}
  & \makecell{\textbf{0.9} $\pm$0.01\\ \Eeog 570 (114)}
  %%
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 150 (14)}
  & \makecell{\textbf{0.52} $\pm$0.03\\ \Eeog 460 (79)}
  & \makecell{\textbf{0.56} $\pm$0.02\\ \Eeog 740 (628)}
  \\
\hline
  $\DG$ vs $\DEG$
  & \makecell{\textbf{0.62} $\pm$0.03\\ \Eeog 410 (7)}
  & \makecell{\textbf{0.6} $\pm$0.02\\ \Eeog 790 (762)}
  & \makecell{\textbf{0.57} $\pm$0.03\\ \Eeog 730 (608)}
  %%
  & \makecell{\textbf{0.46} $\pm$0.03\\ \Eeog 340 (129)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 650 (408)}
  & \makecell{\textbf{0.42} $\pm$0.02\\ \Eeog 690 (467)}
  \\
   \hline
\end{tabular}
\end{adjustbox}
\caption{\footnotesize {\bf Simultaneous Entry}, for Heavy-Tail and Needle-in-Haystack instances. Each cell describes a game between two algorithms, call them Alg1 vs. Alg2, for a particular value of the warm start $T_0$. Line 1 in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG.
Line 2 specifies the ``effective end of game" (\Eeog): the average and the median (in brackets). The time horizon is $T=2000$.}
\label{sim_table}
\end{table*}
\normalsize
Our main experiments are with the duopoly game defined in Section~\ref{sec:model}. As the ``intensity of competition" varies from  monopoly to ``incumbent" to simultaneous entry duopoly to ``late entrant", we find a stylized inverted-U relationship as in Figure~\ref{fig:inverted-U}. More formally, we look for equilibria in the duopoly game, where each firm's choices are limited to \DynamicGreedy, \DynamicEpsGreedy and \Thompson. We do this for each ``intensity level" and each MAB instance, and look for findings that are consistent across MAB instances. For cleaner results, we break ties towards less advanced algorithms (as they tend to have lower adoption costs \cite{DS-arxiv}). Note that \DynamicGreedy is trivially the dominant strategy under monopoly.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
 % \hline
 % & \multicolumn{3}{c|}{Uniform} \\
\hline
   & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\ \hline
\TS vs \DG
  & \makecell{\textbf{0.46} $\pm$0.03}
    & \makecell{\textbf{0.52} $\pm$0.02}
    & \makecell{\textbf{0.6} $\pm$0.02} \\ \hline
\TS vs \DEG
    & \makecell{\textbf{0.41} $\pm$0.03}
    & \makecell{\textbf{0.51} $\pm$0.02}
    & \makecell{\textbf{0.55} $\pm$0.02} \\ \hline
\DG vs \DEG
    & \makecell{\textbf{0.51} $\pm$0.03}
    & \makecell{\textbf{0.48} $\pm$0.02}
    & \makecell{\textbf{0.45} $\pm$0.02} \\\hline
\end{tabular}
\caption{\footnotesize {\bf Simultaneous entry}, for the Uniform MAB instance. Semantics are the same as in Table \ref{sim_table}.}
\label{tab:duopoly_unif}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$
    & \makecell{\textbf{0.003}$\pm$0.003}
    & \makecell{\textbf{0.083}$\pm$0.02}
    & \makecell{\textbf{0.17}$\pm$0.02} \\\hline
$\DEG$
    & \makecell{\textbf{0.045}$\pm$0.01}
    & \makecell{\textbf{0.25}$\pm$0.02}
    & \makecell{\textbf{0.23}$\pm$0.02} \\\hline
$\DG$
    & \makecell{\textbf{0.12}$\pm$0.02}
    & \makecell{\textbf{0.36}$\pm$0.03}
    & \makecell{\textbf{0.3}$\pm$0.02} \\\hline
\end{tabular}
\captionsetup{labelformat=empty}
\caption{\footnotesize Market share of row player (entrant), 200 round head-start, Heavy-Tail Instance}
%\caption{{\bf Temporary monopoly}, with $X=200$ (and $T_0=20$), for the Heavy-Tail MAB instance. Each cell describes the duopoly game between the entrant's algorithm (the row) and the incumbent's algorithm (the column). The cell specifies the entrant's market share (fraction of rounds in which it was chosen) for the rounds in which he was present. We give the average (in bold) and the 95\% confidence interval. NB: smaller average is better for the incumbent.}
\label{tab:ht-incum}
\end{table}
\OMIT{
\begin{table}[h]
\centering
\caption{Heavy Tail}
\begin{tabular}{|c|c|c|c|}
\hline
   & $\TS$  & $\DEG$  & $\DG$ \\ \hline
$\TS$
    & \makecell{\textbf{0.50, 0.50}}
    & \makecell{\textbf{0.3, 0.7}}
    & \makecell{\textbf{0.29, 0.71}} \\\hline
$\DEG$
    & \makecell{\textbf{0.7, 0.3}}
    & \makecell{\textbf{0.50, 0.50}}
    & \makecell{\textbf{0.38, 0.62}} \\\hline
$\DG$
    & \makecell{\textbf{0.71, 0.29}}
    & \makecell{\textbf{0.62, 0.38}}
    & \makecell{\textbf{0.50, 0.50}} \\\hline
\end{tabular}
\end{table}

@@

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}
      \draw[->] (-.5,0) -- (7,0) node[right] {};
      \draw[->] (0,-.5) -- (0,3) node[above] {Better algorithms};
      \draw[scale=0.6,domain=0.7:9.8,smooth,variable=\x,blue, line width=0.3mm] plot ({\x},{4.5 - 0.18 * (\x - 5.25)^2});
     \node[below] at (0.7, -0.22) {\footnotesize monopoly};
     \node[below] at (2.8, -0.2) {\footnotesize incumbent};
     \node[below] at (4.8, -0.22) {\footnotesize sim. entry};
     \node[below] at (6.2, -0.2) {\footnotesize entrant};
 \end{tikzpicture}
 \caption{\footnotesize A stylized ``inverted-U relationship" between strength of competition and ``level of innovation".}
\label{fig:inverted-U-expts}
\end{center}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{ec19paper/figures/unif_eq_welfare}
\includegraphics[scale=0.35]{ec19paper/figures/ht_eq_welfare}
\caption{\footnotesize Smoothed welfare plots resulting from equilibrium strategies in the different market structures. Note that welfare at $t = 0$ incorporates the regret incurred during the incumbent and warm start periods. The Thompson Sampling trajectory displays the regret incurred by running Thompson Sampling in isolation on the given instances.}
\label{eq_regret}
\end{figure}

### 2020-09-04 journal paper/ec19paper/content/non_greedy_choice.tex
update figures

\footnotesize
\begin{table*}[t]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c||}{Heavy-Tail (\HMR with $\eps=.1$)}
  & \multicolumn{3}{c|}{Heavy-Tail (\HM)}\\
  \hline
  & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG
 & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG  \\
  \hline
$T = 2000$
 & \makecell{ \textbf{0.43} $\pm$ 0.02 \\Var: 0.15 }
  & \makecell{ \textbf{0.44} $\pm$ 0.02 \\Var: 0.15 }
  & \makecell{ \textbf{0.6} $\pm$ 0.02 \\Var: 0.1 }
  %%
 &  \makecell{ \textbf{0.29} $\pm$ 0.03 \\Var: 0.2 }
  & \makecell{ \textbf{0.28} $\pm$ 0.03 \\Var: 0.19 }
  & \makecell{ \textbf{0.63} $\pm$ 0.03 \\Var: 0.18 }
    \\
\hline
  $T= 5000$
   & \makecell{ \textbf{0.66} $\pm$ 0.01 \\Var: 0.056 }
  & \makecell{ \textbf{0.59} $\pm$ 0.02 \\Var: 0.092 }
  & \makecell{ \textbf{0.56} $\pm$ 0.02 \\Var: 0.098 }
  %%
 & \makecell{ \textbf{0.29} $\pm$ 0.03 \\Var: 0.2 }
 & \makecell{ \textbf{0.29} $\pm$ 0.03 \\Var: 0.2 }
 & \makecell{ \textbf{0.62} $\pm$ 0.03 \\Var: 0.19 }
 \\
  \hline
  $T = 10000$
  & \makecell{ \textbf{0.76} $\pm$ 0.01 \\Var: 0.026 }
 & \makecell{ \textbf{0.67} $\pm$ 0.02 \\Var: 0.067 }
 & \makecell{ \textbf{0.52} $\pm$ 0.02 \\Var: 0.11 }
 %%
  & \makecell{ \textbf{0.3} $\pm$ 0.03 \\Var: 0.21 }
  & \makecell{ \textbf{0.3} $\pm$ 0.03 \\Var: 0.2 }
  & \makecell{ \textbf{0.6} $\pm$ 0.03 \\Var: 0.2 }
  %%
  \\
   \hline
\end{tabular}
\normalsize
\caption{\HardMax (\HM) and \HardMaxRandom (\HMR) choice models on the Heavy-Tail MAB instance. Each cell describes the market shares in a game between two algorithms, call them Alg1 vs. Alg2, at a particular value of $t$. Line 1 in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG.
Line 2 specifies the variance of the market shares across the simulations. The results reported here are with $T_0 = 20$.}
\label{tab:non_greedy_table}
\end{table*}

@@

\footnotesize
\begin{table*}[t]
\centering
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c||}{Uniform (\HMR  with $\eps=.1$)}
  & \multicolumn{3}{c|}{Needle-In-Haystack (\HMR  with $\eps=.1$)}\\
  \hline
  & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG
 & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG  \\
 \hline
$T = 2000$
 & \makecell{ \textbf{0.42} $\pm$ 0.02 \\Var: 0.13 }
 & \makecell{ \textbf{0.45} $\pm$ 0.02 \\Var: 0.13 }
 & \makecell{ \textbf{0.49} $\pm$ 0.02 \\Var: 0.093 }
  %%
  & \makecell{  \textbf{0.55} $\pm$ 0.02 \\Var: 0.15 }
  & \makecell{  \textbf{0.61} $\pm$ 0.02 \\Var: 0.13 }
  & \makecell{  \textbf{0.46} $\pm$ 0.02 \\Var: 0.12 }
    \\
\hline
  $T= 5000$
 & \makecell{ \textbf{0.48} $\pm$ 0.02 \\Var: 0.089 }
 & \makecell{ \textbf{0.53} $\pm$ 0.02 \\Var: 0.098 }
 & \makecell{ \textbf{0.46} $\pm$ 0.02 \\Var: 0.072 }
  %%
 & \makecell{  \textbf{0.56} $\pm$ 0.02 \\Var: 0.13 }
 & \makecell{  \textbf{0.63} $\pm$ 0.02 \\Var: 0.12 }
 & \makecell{  \textbf{0.43} $\pm$ 0.02 \\Var: 0.11 }
 \\
  \hline
  $T = 10000$
& \makecell{ \textbf{0.54} $\pm$ 0.01 \\Var: 0.055 }
& \makecell{  \textbf{0.6} $\pm$ 0.02 \\Var: 0.073 }
& \makecell{  \textbf{0.44} $\pm$ 0.02 \\Var: 0.064 }
 %%
  & \makecell{ \textbf{0.58} $\pm$ 0.02 \\Var: 0.083 }
  & \makecell{ \textbf{0.65} $\pm$ 0.02 \\Var: 0.096 }
  & \makecell{ \textbf{0.4} $\pm$ 0.02 \\Var: 0.1 }
  %%
  \\
   \hline
\end{tabular}
\caption{\HardMaxRandom (\HMR) choice model for Uniform and Needle-In-Haystack MAB instances.}
%Same semantics as in Table \ref{tab:non_greedy_table}.
\label{tab:additional_results}
\end{table*}
\normalsize

>>>>

\footnotesize
\begin{table*}[t]
\centering
\begin{adjustbox}{width=\textwidth,center}
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c||}{Heavy-Tail (\HMR with $\eps=.1$)}
  & \multicolumn{3}{c|}{Heavy-Tail (\HM)}\\
  \hline
  & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG
 & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG  \\
  \hline
$T = 2000$
 & \makecell{ \textbf{0.43} $\pm$ 0.02 \\Var: 0.15 }
  & \makecell{ \textbf{0.44} $\pm$ 0.02 \\Var: 0.15 }
  & \makecell{ \textbf{0.6} $\pm$ 0.02 \\Var: 0.1 }
  %%
 &  \makecell{ \textbf{0.29} $\pm$ 0.03 \\Var: 0.2 }
  & \makecell{ \textbf{0.28} $\pm$ 0.03 \\Var: 0.19 }
  & \makecell{ \textbf{0.63} $\pm$ 0.03 \\Var: 0.18 }
    \\
\hline
  $T= 5000$
   & \makecell{ \textbf{0.66} $\pm$ 0.01 \\Var: 0.056 }
  & \makecell{ \textbf{0.59} $\pm$ 0.02 \\Var: 0.092 }
  & \makecell{ \textbf{0.56} $\pm$ 0.02 \\Var: 0.098 }
  %%
 & \makecell{ \textbf{0.29} $\pm$ 0.03 \\Var: 0.2 }
 & \makecell{ \textbf{0.29} $\pm$ 0.03 \\Var: 0.2 }
 & \makecell{ \textbf{0.62} $\pm$ 0.03 \\Var: 0.19 }
 \\
  \hline
  $T = 10000$
  & \makecell{ \textbf{0.76} $\pm$ 0.01 \\Var: 0.026 }
 & \makecell{ \textbf{0.67} $\pm$ 0.02 \\Var: 0.067 }
 & \makecell{ \textbf{0.52} $\pm$ 0.02 \\Var: 0.11 }
 %%
  & \makecell{ \textbf{0.3} $\pm$ 0.03 \\Var: 0.21 }
  & \makecell{ \textbf{0.3} $\pm$ 0.03 \\Var: 0.2 }
  & \makecell{ \textbf{0.6} $\pm$ 0.03 \\Var: 0.2 }
  %%
  \\
   \hline
\end{tabular}
\end{adjustbox}
\caption{\footnotesize \HardMax (\HM) and \HardMaxRandom (\HMR) choice models on the Heavy-Tail MAB instance. Each cell describes the market shares in a game between two algorithms, call them Alg1 vs. Alg2, at a particular value of $t$. Line 1 in the cell is the market share of Alg 1: the average (in bold) and the 95\% confidence band.
%For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG.
Line 2 specifies the variance of the market shares across the simulations. The results reported here are with $T_0 = 20$.}
\label{tab:non_greedy_table}
\end{table*}

@@

\footnotesize
\begin{table*}[t]
\centering
\begin{adjustbox}{width=\textwidth,center}
\begin{tabular}{|c|c|c|c||c|c|c|}
  \hline
  & \multicolumn{3}{c||}{Uniform (\HMR  with $\eps=.1$)}
  & \multicolumn{3}{c|}{Needle-In-Haystack (\HMR  with $\eps=.1$)}\\
  \hline
  & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG
 & \TS vs \DG & \TS vs \DEG  & \DG vs \DEG  \\
 \hline
$T = 2000$
 & \makecell{ \textbf{0.42} $\pm$ 0.02 \\Var: 0.13 }
 & \makecell{ \textbf{0.45} $\pm$ 0.02 \\Var: 0.13 }
 & \makecell{ \textbf{0.49} $\pm$ 0.02 \\Var: 0.093 }
  %%
  & \makecell{  \textbf{0.55} $\pm$ 0.02 \\Var: 0.15 }
  & \makecell{  \textbf{0.61} $\pm$ 0.02 \\Var: 0.13 }
  & \makecell{  \textbf{0.46} $\pm$ 0.02 \\Var: 0.12 }
    \\
\hline
  $T= 5000$
 & \makecell{ \textbf{0.48} $\pm$ 0.02 \\Var: 0.089 }
 & \makecell{ \textbf{0.53} $\pm$ 0.02 \\Var: 0.098 }
 & \makecell{ \textbf{0.46} $\pm$ 0.02 \\Var: 0.072 }
  %%
 & \makecell{  \textbf{0.56} $\pm$ 0.02 \\Var: 0.13 }
 & \makecell{  \textbf{0.63} $\pm$ 0.02 \\Var: 0.12 }
 & \makecell{  \textbf{0.43} $\pm$ 0.02 \\Var: 0.11 }
 \\
  \hline
  $T = 10000$
& \makecell{ \textbf{0.54} $\pm$ 0.01 \\Var: 0.055 }
& \makecell{  \textbf{0.6} $\pm$ 0.02 \\Var: 0.073 }
& \makecell{  \textbf{0.44} $\pm$ 0.02 \\Var: 0.064 }
 %%
  & \makecell{ \textbf{0.58} $\pm$ 0.02 \\Var: 0.083 }
  & \makecell{ \textbf{0.65} $\pm$ 0.02 \\Var: 0.096 }
  & \makecell{ \textbf{0.4} $\pm$ 0.02 \\Var: 0.1 }
  %%
  \\
   \hline
\end{tabular}
\end{adjustbox}
\caption{\footnotesize \HardMaxRandom (\HMR) choice model for Uniform and Needle-In-Haystack MAB instances.}
%Same semantics as in Table \ref{tab:non_greedy_table}.
\label{tab:additional_results}
\end{table*}
\normalsize

### 2020-09-04 journal paper/ec19paper/content/perf_in_iso.tex
update figures

\begin{figure}
\centering
\includegraphics[scale=0.35]{ec19paper/figures/nih_mean}
\includegraphics[scale=0.35]{ec19paper/figures/mean_inst_reward_nih}
%\caption*{\tiny{Mean reputation trajectory The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. The shaded area display 95\% confidence intervals.}}
\caption{Mean reputation trajectory (left) and mean instantaneous reward trajectory (right) for Needle-in-Haystack. The shaded area shows 95\% confidence intervals.}
\label{prelim_means}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{ec19paper/figures/relative_nih_ts_dg}
%\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\Thompson \geq \DynamicGreedy$. The shaded area display 95\% confidence intervals.}}
\caption{Relative reputation trajectory for $\Thompson$ vs $\DynamicGreedy$, on Uniform instance (left) and Needle-in-Haystack instance (right). Shaded area display 95\% confidence intervals.}
\label{relative_rep_plots}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.35]{ec19paper/figures/nih_mean}
\includegraphics[scale=0.35]{ec19paper/figures/mean_inst_reward_nih}
%\caption*{\tiny{Mean reputation trajectory The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. The shaded area display 95\% confidence intervals.}}
\caption{\footnotesize Mean reputation trajectory (left) and mean instantaneous reward trajectory (right) for Needle-in-Haystack. The shaded area shows 95\% confidence intervals.}
\label{prelim_means}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{ec19paper/figures/relative_nih_ts_dg}
%\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\Thompson \geq \DynamicGreedy$. The shaded area display 95\% confidence intervals.}}
\caption{\footnotesize Relative reputation trajectory for $\Thompson$ vs $\DynamicGreedy$, on Uniform instance (left) and Needle-in-Haystack instance (right). Shaded area display 95\% confidence intervals.}
\label{relative_rep_plots}
\end{figure}

### 2020-09-04 journal paper/ec19paper/content/revisited.tex
update figures

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/rep_distribution_nih}
\includegraphics[scale=0.35]{ec19paper/figures/ts_dg_rep_diff_nih}
\caption{Reputation scores for Needle-in-Haystack at $t=500$ (left), Reputation difference $\Thompson - \DynamicGreedy$ for Needle-in-Haystack (right). Both are smoothed using a kernel density estimate.}
\label{fig:rep_dist_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the reputation distribution at $t = 500$}}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[scale=0.35]{ec19paper/figures/rep_distribution_nih}
\includegraphics[scale=0.35]{ec19paper/figures/ts_dg_rep_diff_nih}
\caption{\footnotesize Reputation scores for Needle-in-Haystack at $t=500$ (left), Reputation difference $\Thompson - \DynamicGreedy$ for Needle-in-Haystack (right). Both are smoothed using a kernel density estimate.}
\label{fig:rep_dist_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the reputation distribution at $t = 500$}}
\end{figure}
